---
title: "The presention on presentaion"
subtitle: " The subtitle for the presentiton"
auther: ' Diesel Wing'
date: "12/06/2019"
output:
  revealjs::revealjs_presentation:
#    center: yes # centres vertically
#    css: gk_css.css # works but was badly desinged
    fig_caption: yes
    fig_height: 5
    fig_width: 10
    highlight: "pygments" # NULL, "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock"
    toc: TRUE  # but not coming
#    incremental: yes  # better use -<
    reveal_options:
      previewLinks: yes
      slideNumber: yes
    self_contained: no
   # smart: TRUE
    theme: "solarized" # "default", "simple", "sky", "beige", "serif", "solarized", "blood", "moon", "night", "black", "league" or "white"
    transition: "default" #"default", "fade", "slide", "convex", "concave", "zoom" or "none".
    background_transition: "convex" #"default", "fade", "slide", "convex", "concave", "zoom" or "none"

#  prettydoc::html_pretty:
#    highlight: github
#    theme: cayman
  reveal_plugins:
    #  - notes
    #  - search
    #  - chalkboard
---

<!---
# override global transition by data-transition attribute, for example:
## Use a zoom transition {data-transition="zoom"}
## faster speed {data-transition-speed="fast"}

## Fade in, Slide out {data-transition="slide-in fade-out"}
## Slide in, Fade out {data-transition="fade-in slide-out"}

## CSS color background {data-background=#ff0000}
## image background {data-background="background.jpeg"}
## Video background {data-background-video="background.mp4"}
## Webpage background {data-background-iframe="https://example.com"}
--->


# Reason for this presentation

The purpose is :

  > - Keep workable templete for use
  > - Keep on improving it in github
  
# optons in r chunks

- cache: cache results for future knits (default = FALSE)
- cache.path: directory (default = “cache/”)
- child: file(s) to knit and then include (default = NULL)
- collapse: collapse all output into single block (default = FALSE)
- comment: prefix for each line of results (default = ‘##’)
- dependson: chunk dependencies for caching (default = NULL)

## Other normal 

- echo: (default = TRUE) ;
- engine: (default = ‘R’)
- error:  (default = FALSE)
- warning: display code warnings in document (default = TRUE)
- message: (default = TRUE)
- eval:  (default = TRUE)

## other 3
- results=asis: passthrough results
- results=hide: do not display results
- results=hold: put all results below all code
- tidy: tidy code for display (default = FALSE)



## figures

- fig.align: ‘lef’, ‘right’, or ‘center’ (default = ‘default’)
- fig.cap: figure caption as character string (default = NULL)
- fig.height, fig.width: Dimensions of plots in inches
- highlight: highlight source code (default = TRUE)
- include: Include chunk in doc after running (default = TRUE)

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

---

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets


- Bullet 1
- Bullet 2
- Bullet 3

# Tables

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
data <- faithful[1:4, ]
knitr::kable(data, caption = 'Table with kable')
```

## Another talbe


```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}

data <- faithful[1:4, ]
print(xtable::xtable(data, caption = 'Table with xtable'), type = 'HTML', 
      HTML.table.attributes = 'border=0')
```

## yet another talbe

```{r, echo = FALSE, eval=TRUE, include=TRUE, error=FALSE, warning=FALSE, message=FALSE}
library(stargazer)
data <- faithful[1:4, ]
stargazer::stargazer(data, type = 'HTML', title = 'Table with stargazer')

```



# A background page {data-background-iframe="https://rdso.indianrailways.gov.in"}



# CSS color background {data-background=#ff0000 }

 1. some dummy text 
 2. some other text
 2. Yet another text
 
# Full size image background {data-background="img/corona19.jpg" } 

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(ggpubr)
# Grouped Scatter plot with marginal density plots
ggscatterhist(
  iris, x = "Sepal.Length", y = "Sepal.Width",
  color = "Species", size = 3, alpha = 0.6,
  palette = c("#00AFBB", "#E7B800", "#FC4E07"),
  margin.params = list(fill = "Species", color = "black", size = 0.2)
  ) + theme_transparent()
```  

# Video background {data-background-video="demo.mp4"}

  - This is some text
  - some onther text
  - Yet some another text
  
# Embed a web page as a background {data-background-iframe="https://example.com"}

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library("ggalt")
ggplot(mtcars, aes(mpg, wt)) +
  geom_point( aes(size = qsec , fill = cyl ), alpha = 0.5) +
  scale_size(range = c( 0.5,  12 ))  # Adjust the range of points size
```  

  1. Depite bg another text
  2. some another text

# Slide with R Code and Output

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library("ggalt")
circle.df <- iris %>% filter(Species == "setosa")
ggplot(iris, aes(Petal.Length, Petal.Width)) +
    geom_point(aes(colour = Species)) + 
  geom_encircle(data = circle.df, linetype = 2)
```

## Slide with Plot

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(ggforce)
ggplot(iris, aes(Petal.Length, Petal.Width, colour = Species)) +
    geom_point() +
    facet_zoom(x = Species == "versicolor")
```

# The top p head



# Background Three {.SlideClass #SlideID3}

Full screen background

```{r results='asis', echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}

#makeBG(id='Slide3', 'figure2b.png')
```


```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
Sys.setlocale("LC_CTYPE", "russian")
#st_options(lang = 'ru')
#Then, to go back to default settings:

Sys.setlocale("LC_CTYPE", "")
#st_options(lang = "en")
```



## table

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- mtcars[1:5, 1:6]

iris[1:10, ] %>%
  mutate_if(is.numeric, function(x) {
    cell_spec(x, bold = T, 
              color = spec_color(x, end = 0.9),
              font_size = spec_font_size(x))
  }) %>%
  mutate(Species = cell_spec(
    Species, color = "white", bold = T,
    background = spec_color(1:10, end = 0.9, option = "A", direction = -1)
  )) %>%
  kable(escape = F, align = "c") %>%
  kable_styling(c("striped", "condensed"), full_width = F)

kable(dt) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_right", font_size = 7)


```

# some more slide

## combineing formatable with 

```{r, echo = FALSE, eval=TRUE,  error=FALSE, warning=FALSE, message=FALSE}
library(formattable)
mtcars[1:5, 1:4] %>%
  mutate(
    car = row.names(.),
    mpg = color_tile("white", "orange")(mpg),
    cyl = cell_spec(cyl, angle = (1:5)*60, 
                    background = "red", color = "white", align = "center"),
    disp = ifelse(disp > 200,
                  cell_spec(disp, color = "red", bold = T),
                  cell_spec(disp, color = "green", italic = T)),
    hp = color_bar("lightgreen")(hp)
  ) %>%
  select(car, everything()) %>%
  kable(escape = F) %>%
  kable_styling("hover", full_width = F) %>%
  column_spec(5, width = "3cm") %>%
  add_header_above(c(" ", "Hello" = 2, "World" = 2))
```

# Thank you

Thank you very much
